NN_Accel_Heading

### 2024-03-15 Fish Data Analysis/NN_Accel_Heading.qmd
Single fish plotting works

single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>% mutate(Type = "Single")

@@

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup() %>% mutate(Type = "Eight")

@@

@@

min_dist <- sd*0.5
max_dist <- sd*1.5

@@

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  # geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
  #                 ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
  #                 fill = interaction(Ablation, Darkness, sep =", ")),
  #             alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-100,100) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)

@@

@@

>>>>

single_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "Jingle")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Single", "Jingle")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           # # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           #filter(row_number() %% 3 == 1) %>%
                           ungroup() %>%
                           mutate(Type = "Single")

@@

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           #filter(row_number() %% 3 == 1) %>%
                           ungroup() %>%
                           mutate(Type = "Eight")

@@

ggplot(fish_comp_data, aes(x = Angle))+
  geom_histogram()+
  facet_wrap(~Flow_Ablation_Darkness)

@@

min_dist <- 0.75 #sd*0.5
max_dist <- 3 #sd*1.5

@@

Distribution of turning velocities at say 90 degrees
just make a Kolmogorov–Smirnov to compare distribution. See if distribution is different
  Not larger or smaller?
Also maybe just do a t test 
trim the edge points

too much variance, not significant

@@

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes( y = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA)) ), size = 1)+
  geom_ribbon(aes(ymin = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) - se),
                  ymax = rad2deg(predict(manual_model,newdata = graph_model_data, re.form = NA) + se),
                  fill = interaction(Ablation, Darkness, sep =", ")),
              alpha = 0.25, colour = NA)+
  theme_classic() +
  ylim(-100,100) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+ 
  guides(fill = FALSE)

@@

plot(manual_model)
qqnorm(resid(manual_model))
#qqline(resid(groups_lmer_flow))

@@

Removing underlying variation to the data?

tank_data <- fish_comp_data %>% filter(Flow == "Still Water") %>% 
                                mutate(Round_X = round_any(Fish1_X,1),
                                       Round_Y = round_any(Fish1_Y,1)) %>%
                                group_by(Flow_Ablation_Darkness, Round_X, Round_Y) %>%
                                summarise(Mean_HPS = mean(Fish1_Yaw_Heading_PS)) %>%
                                ungroup()

ggplot(tank_data , aes(Round_X, Round_Y, fill = Mean_HPS))+
  facet_wrap(~ Flow_Ablation_Darkness)+
  geom_tile()+
  theme_classic()
